---
title: "Cleaning Nigeria Budget Data"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, python.reticulate = T}
```


```{r, python.reticulate = T}
# for y in [1, 2, 3]:
#   print(y)
```

##Read the data
```{r , echo=T}
library(tidyverse)
library(knitr)
raw_2021_budget_2021 <-
  read_csv(
    "PDF_Data/raw_2021_budget_2021.csv"
  )
raw_2021_budget_2021
```

## Overiew
Let's make a copy of the original data
```{r}
data__2021_start <- raw_2021_budget_2021 
```

### Inspection
We inspect our to see the each colum to see how many empty rows they contain. In what follows, `map_dl()` map the datafrme `data__2021_start` in to a vector using an anonymous function 
that calculates the percentage of empty record contain in each column. `length()` returns the size of what (`which()`) empty (`is.na()`) rows(`(.)`) are contained in each column; mutiplies it by 100 and rounds (`round()`) it to the nearest whole number.
```{r}
data__2021_start %>% map_dbl(function(x) round(100*length(which(is.na(x)))/length(x))) 
```
This shows that bulk of the data is in `Data.Column1`, `Data.Column2` and `Data.Column3` since they contain just 11%, 1% and 6% null rows respectively.

When extracting the tables form Excel, the `Id`, `Name` and `Kind` Columns were automatically created to be used for identifying the table in the pdf that was converted to excel. That affors us an advatage. Since the Id column is serial, we can use it to sort (`arrange()`) our table in such a way that it matches the order of tables in the original document. And to double check, we also add the column `Data.Column1` to the sort criteria.

```{r}
data__2021_start %>% arrange(Id, Data.Column1)
```

The big question is how do we structure our data so that it can produce the same figure, with 0% error tolerance?
Let us explore the least units of our data. By observation, the records are stored on hierachical level; with 48 Ministries Department and Agencies (MDA's). Under each MDA, there are sub-MDA'S. The take-away, however is that for all sub divisions their expenditure is made of 2 of these 3 cost elements, namely, `CAPITAL EXPENDITURE`, `OTHER RECURRENT COSTS`,`PERSONNEL COST`. We shall Explain the reason for the inclusion of `TOTAL RETAINED INDEPENDENT REVENUE` later.
```{r}
library(collapsibleTree)
data__2021_test =read_csv("Budget_Data/data__2021_test.csv")
data__2021_test <- data__2021_test %>% filter(costCenter_Code=="0111") %>% 
  group_by( costCenter_Code_MDA, table_identifier_MDA, lineExpTermLevel1, lineExpTermLevel2)  %>% 
  summarise(Amount=sum(Amount))
data__2021_test %>% collapsibleTree(c("costCenter_Code_MDA", "table_identifier_MDA", "lineExpTermLevel1"))
kable(data__2021_test)
```

